---
output: 
  github_document:
    pandoc_args: --webtex=https://chart.apis.google.com/chart?cht=tx&chl=
---

# Smooth lines for Standardised Major Axis (SMA) Regression 

![R-CMD-check](https://github.com/mattocci27/ggsma/workflows/R-CMD-check/badge.svg?branch=master)

## Installation

````{r,eval=FALSE}
devtools::install_github("mattocci27/ggsma")
````

````{r,eval=FALSE, echo=FALSE}
rmarkdown::render("README.Rmd")
````

## Function

- `geom_sma()`: draws fitted lines based on SMA.

## SMA (blue) vs OLS (red)

```{r}
library(ggplot2)
library(ggsma)
library(smatr)

data(leaflife)
head(leaflife)
leaf_low <- subset(leaflife, soilp == "low")

# lma vs longev only for low soilp sites
ggplot(leaf_low, aes(lma, longev)) +
  geom_point() +
  geom_sma() +
  geom_smooth(method = "lm", col = "red") 
```

```{r}
# facet for low and high rain sites 
ggplot(leaflife, aes(lma, longev)) +
  geom_point() +
  geom_sma() +
  geom_smooth(method = "lm", col = "red")  +
  facet_wrap( ~ rain)
```

## Only shows significant relationships 

```{r}
# weakly correlated data
library(tidyverse)
set.seed(1234)
S <- clusterGeneration::genPositiveDefMat(5)$Sigma
Cor <- cov2cor(S)
Cor[1, 5] <- Cor[5, 1] <- 0.8
Cor %>% round(2)

dat <- mvtnorm::rmvnorm(30, mean = rep(0, 5),  sigma = Cor) 
colnames(dat) <- c("y", paste0("x", 1:4))

dat_long <- dat %>%
  as_tibble %>%
  pivot_longer(2:5)

ggplot(dat_long, aes(x = value, y = y, col = name)) +
  geom_point() +
  geom_sma()

# shows non-significant relationships using dased lines
ggplot(dat_long, aes(x = value, y = y, col = name)) +
  geom_point() +
  geom_sma(show.sig.only = 1)

# only keeps significant relationships 
ggplot(dat_long, aes(x = value, y = y, col = name)) +
  geom_point() +
  geom_sma(show.sig.only = 2)

```

Of course, we can do the same thing without using `show.sig.only` argument but
need a little bit more work.

```{r}
dat_long2 <- dat_long %>%
  group_by(name) %>%
  nest() %>%
  mutate(p = map_dbl(data, ~ cor.test(.$y, .$value)$p.value)) %>%
  unnest(cols = c(data))

ggplot(dat_long2, aes(x = value, y = y, col = name)) +
  geom_point() +
  geom_sma(data = dat_long2 %>% filter(p < 0.05)) +
  geom_sma(data = dat_long2 %>% filter(p > 0.05),
           lty = 2, se = FALSE)
```

## Reference

Warton, David I., Ian J. Wright, Daniel S. Falster, and Mark Westoby. 2006. Bivariate Line-Fitting Methods for Allometry. Biological Reviews 81: 259–91. [https://doi.org/10.1017/S1464793106007007](https://doi.org/10.1017/S1464793106007007)
